---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

# amregtest

<!-- badges: start -->
<!-- badges: end -->

"`amregtest`" stands for "`allelematch` regression test".
[`allelematch`](https://cran.r-project.org/package=allelematch) is an R package
for identifying and removing duplicate multilocus genotypes from microsatellite
data sets. `amregtest` verifies that `allelematch` remains backwards compatible
across versions.

By decoupling the regression test suite from the main `allelematch` source code
and its specific `testthat` dependencies, `amregtest` allows you to run
regression tests against *any* version of `allelematch` without modifying the
package under test.

## Installation

You can install the development version of `amregtest` from GitHub with:

```r
# install.packages("devtools")
devtools::install_github("torstax/amregtest")
```

## Usage

```{r libraries}
library(allelematch)
library(amregtest)
```

Run the full regression test suite against your currently installed version of
`allelematch` (takes a few minutes):

```{r run-all, fig.show='hide', results='hold', cache=TRUE}
artRun()
```

To run only tests whose names match a Perl regular expression:

```{r run-filter, fig.show='hide', results='hold'}
artRun(filter = "amExample2|amExample4")
```

List all available tests without running them:

```{r list}
artList()
```

Check the installed versions of `allelematch` and `amregtest`:

```{r version}
artVersion()
```
